Quality Assesment of OpenStreetMap Footpath Data for 3D City Recreation

### 2020-05-13 report/report.tex
Remove blindtext from abstract
Shorten abstract

\usepackage{blindtext} % This is just to get some nonsense text in this template, can be safely removed

@@

  An estimate of the positional accuracy of OSM data has been obtained by comparing OSM positional data to a dataset with a known accuracy, which was obtained from the Swedish National Land Survey.
It was found that the average positional error in the OSM dataset was about 2 meters, and approximately 98\% of all buildings in the reference dataset were represented in the OSM dataset.

  This estimate of the positional error was used to assess the integrity of the OSM Stockholm road network, by locating critical points where assigning widths to the roads would cause collision with other features.
  An algortitm then took the road network and made adjustments that were within the found margin of error for the OSM dataset, to eliminate as many collisions as possible.
  It was found that extending all roads with a standard width led to collisions between roughly 12\% of all roads in the dataset.
  The total length of road that intersected with other features was less than 0.1\% of the total road length.
  It was measured that roughly 80\% of these colliding features, and 99\% of the colliding road by length, could be corrected by simple geometrical translation by a distance smaller than the posiional accuracy of the OSM dataset.
  It was found that footpaths were much less problematic than other road types (primary, secondary, residential), in terms of feature collisions.

  The report concludes with a discussion of the findings of this study, and an assessment of the feasibility of generating city models with pedestrian footpaths in a number of different applications from urban planning tools to videogames.
  As secondary contributions, the completeness and shape accuracy of the OSM data set have also been estimated and commented.

  \blindtext
\end{abstract}

>>>>

@@

An estimate of the positional accuracy of OSM data has been obtained by comparing OSM positional data to a dataset with a known accuracy, which was obtained from the Swedish National Land Survey.
It was found that the average positional error in the OSM dataset was about 2 meters.
This estimate of the positional error was then used to assess the integrity of the OSM Stockholm road network, by locating critical points where assigning standard widths to the roads would cause collision with other features, and evaluating how many of those points could be eliminated by making ajustments within the found margin of error.

It was found that extending all roads with widths led to collisions between roughly 12\% of all roads in the dataset, and the length of road that intersected with other features was less than 0.1\% of the total road length.
Roughly 80\% of these colliding features, and 99\% of the colliding road by length, could be corrected.
It was found that footpaths were less problematic than other road types (primary, secondary, residential), in terms of feature collisions, and thus should pose no more problems in 3D city reproduction than other road types.

The report concludes with a discussion of the findings of this study, and an assessment of the feasibility of generating city models with pedestrian footpaths in a number of different applications from urban planning tools to videogames.
\end{abstract}
